Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-09-09 writeup/gz_hubble_data.tex
Highlight changes

\subsection{Effects of morphological debiasing}\label{ssec:zeta_results}
The approach used in GZH for correcting the weighted classifications for
redshift bias rests on the assumption that the \emph{degree} of bias is a
function of the apparent size and brightness of the galaxy.
This is controlled by two types of parameters: \textbf{intrinsic} properties of
the galaxy itself, such as its physical diameter and luminosity, and
\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
and its relative orientation. The combination of all
such parameters forms a high-dimensional space, \changes{and there is no obvious technique
for separating these into individual effects}. Instead, the method used here employs
only two parameters as a simple model of the effect of redshift brightness on classification: the
surface brightness ($\mu$; intrinsic) and redshift ($z$;
extrinsic).

@@

\subsection{Correcting morphologies for classification bias}\label{ssec:zeta}

@@

\begin{equation}
f_{\mu,z} = 1 - (1 - f_{\mu,z=0.3})e^{\frac{z-z_0}{\hat\zeta}}
\label{eqn:fzeta}
\end{equation}

%old equation
%We model the debiased vote fraction $f_{\mu,z}$ for an
%artificially-redshifted galaxy as:

@@

\noindent where $f_{\mu,z=0.3}$ is the vote fraction at the lowest redshift in
the artificially-redshifted sample ($z_0=0.3$). Here, $\zeta$ is a parameter that
controls the rate at which \ffeatures{} decreases with increasing redshift (and
that may depend on other galaxy properties). This function bounds the observed
vote fractions between $f_{\mu,z=0.3}$ and zero based on two assumptions: 1)
the vote fractions for featured galaxies decrease monotonically with increasing
redshift, therefore restricting vote fractions for a given galaxy to be less
than $f_{\mu,z=0.3}$ (which is almost always true of the data), and 2) the
vote fractions cannot be less than zero (which is always true).

>>>>

\changes{\subsection{Effects of morphological debiasing}\label{ssec:zeta_results}}
The approach used in GZH for correcting the weighted classifications for
redshift bias rests on the assumption that the \emph{degree} of bias is a
function of the apparent size and brightness of the galaxy.
This is controlled by two types of parameters: \textbf{intrinsic} properties of
the galaxy itself, such as its physical diameter and luminosity, and
\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
and its relative orientation. The combination of all
such parameters forms a high-dimensional space, \changes{and there is no obvious technique
for separating these into individual effects}. Instead, the method used here employs
only two parameters as a simple model of the effect of redshift brightness on classification: the
surface brightness ($\mu$; intrinsic) and redshift ($z$;
extrinsic).

@@

\changes{\subsection{Correcting morphologies for classification bias}\label{ssec:zeta}}

@@

\changes{
\begin{equation}
f_{\mu,z} = 1 - (1 - f_{\mu,z=0.3})e^{\frac{z-z_0}{\hat\zeta}}
\label{eqn:fzeta}
\end{equation}
}
%old equation
%We model the debiased vote fraction $f_{\mu,z}$ for an
%artificially-redshifted galaxy as:

@@

\noindent \changes{where $f_{\mu,z=0.3}$ is the vote fraction at the lowest redshift in
the artificially-redshifted sample ($z_0=0.3$). Here, $\zeta$ is a parameter that
controls the rate at which \ffeatures{} decreases with increasing redshift (and
that may depend on other galaxy properties). This function bounds the observed
vote fractions between $f_{\mu,z=0.3}$ and zero based on two assumptions: 1)
the vote fractions for featured galaxies decrease monotonically with increasing
redshift, therefore restricting vote fractions for a given galaxy to be less
than $f_{\mu,z=0.3}$ (which is almost always true of the data), and 2) the
vote fractions cannot be less than zero (which is always true).}
